---
title: "Quizz Course 2 Week 1"
author: "jtracos"
date: "25/1/2021"
output: html_document
---
# Obtaining the data
We got the data from coursera. The dataset contains weather records from somewhere location; we need get knowledge
of data:
```{r getdata, echo=FALSE}
#source("../Data/scripts/Analisis_Descriptivo_MetDatos.R", echo = FALSE)

```
## Preparing Filtering(I)
We made three function to analyze the data, for filtering, mainly
  
1:We need to know the max and mean of data on *Ozone > 31* and *Temp >90*. 
```{r}
getDataClean<- function(data)
  {
  ## funcion para obtener los valores que cumplen con las condiciones
  # count lost data on Ozone
  n_na <- is.na(data$Ozone)
  print("# NA on Ozone Attr:")
  print(sum(n_na==TRUE))
  # get complete data
  cond1 <- data$Ozone>31
  cond2 <- data$Temp>90
  #condition to apply
  good <- cond1 || cond2
  return( data[good,])
}
```
and  2 and 3: Basically, to filter data based on a particular month and get the summary
```{r}
getDatabyMonth <- function(data, month)
  {
  #attach(data)
  idx <- data$Month == month
  return(data[idx,])
}
showResults<-function(data)
  {
  print("summary of selected data:")
  print(summary(data))
}
```
## Carga de datos


Now, we load and apply the function to get the data summary

```{r readdata, echo=TRUE}
path ="../Data/hw1_data.csv"
rough_data <- read.csv(path)
good <- complete.cases(rough_data)
clean_data = rough_data[good,]
data_month6 <- getDatabyMonth(clean_data, month = 6)
data_month5 <- getDatabyMonth(clean_data, month = 5)
```
We got the results for the fifth month:
```{r mayo, echoTRUE}
showResults(data_month5)
```
And, for the sixth month:
```{r junio, echoTRUE}
showResults(data_month6)
```
wait... What happened with the first function??!!
well... These are the stats from the subset belonging to when *Ozone greater than 31* or *Temperature greater than 90*
```{r summarycond, echo= TRUE}
data_filt <- getDataClean(rough_data)
```
```{r}
showResults(data_filt)
```

